---
title: "Real Time Sentiment Analysis of tweets"
output:
  html_document:
    df_print: paged
---

Loading the packages
```{r}
library(base)
# package to download tweets
library(rtweet)
# plotting and pipes - tidyverse not tidytext
library(ggplot2)
#library(dplyr)
# plotting packages
library(igraph)
library(ggraph)
# Packages for sentiment Analysis
library(sentimentr)
library(SentimentAnalysis)

```


#### Loading tweets for a certain period for the topic Election

```{r}

pres_tweets3<- search_tweets(q = "Election", n = 15000,lang = "en",include_rts = FALSE, retryonratelimit = TRUE)

```
#### First 15 tweets

```{r}
pres_tweets3$text[1:15]
```

## Preprocessing:

#### Remove http and https from tweets

```{r}
pres_tweets3$stripped_text <- gsub("http.*","",  pres_tweets3$text)
pres_tweets3$stripped_text <- gsub("https.*","", pres_tweets3$stripped_text)
```

#### Convert tweets to lower case

```{r}
pres_tweets3$stripped_text=tolower(pres_tweets3$stripped_text)
```

#### Analyze the tweets. This includes removing stopwords and stemming the words


```{r}
pres_tweets3$sent <- analyzeSentiment(pres_tweets3$stripped_text, language = "english",aggregate = NULL, removeStopwords = TRUE, stemming = TRUE)


```

#### Get a binary response that is if tweet is either positive or negative


```{r}
pres_tweets3$posneg<-convertToBinaryResponse(pres_tweets3$sent)$SentimentGI
```

##### Create the label position

```{r}
pres_tweets3$sent$label_sentiment <- pres_tweets3$sent$SentimentGI +0.015
```

#### Plot the total number of positives and negatives over all tweets

```{r}
plot(pres_tweets3$posneg, xlab="Negatives and Positives", ylab="Count", main="Total positives and negatives for 18000 tweets on Election", col = c("red", "blue"))
```

#### Adding plot label positions for points

```{r}
pres_tweets3$sent$label_sentiment <- pres_tweets3$sent$SentimentGI +0.015
```

#### Plot for 100 tweets

```{r}
plot(pres_tweets3$sent$SentimentGI[1:100], y =NULL, type = "o", xlab = "Tweet index", ylab = "Negative to Positive",main = " Positive Negative plots for 100 tweets fro the topic Election")
text(x=pres_tweets3$sent$label_sentiment[1:100],y=
       NULL,labels=pres_tweets3$posneg[1:100])

```

#### Plot for 18000 tweets

```{r}
plot(pres_tweets3$sent$SentimentGI, y =NULL, type = "o", xlab = "Tweet index", ylab = "Negative to Positive",main = " Positive Negative plots for 18000 tweets on Election")
text(x=pres_tweets3$sent$label_sentiment,y=
       NULL,labels=pres_tweets3$posneg)
```

### Plotting sentiment values across tweets as a histogram

```{r}

hist(pres_tweets3$sent$SentimentGI, xlab ="Sentiment Value" , ylab = "Tweet Count", main = "Sentiment value across tweets",col=("mediumpurple1"))
```
#### Split text of all tweets by sentences

```{r}
split_text3 <- get_sentences(pres_tweets3$text)

```

#### Get emotion for overall tweets using the sentences we got above

```{r}
(emo3 <- emotion(split_text3))

```

#### Drop unused emotions

```{r}
emotion(split_text3, drop.unused.emotions = TRUE)

```

#### Plot emotions over all tweets. We notice a difference from the previous set of tweets

```{r}

plot(emo3)

```

#### Plotting with unused emotions being dropped (We notice there is not a major difference)

```{r}

plot(emo3, drop.unused.emotions = FALSE)

```

#### Plot of all emotions together

```{r}

plot(emo3, facet = FALSE)

```

#### Plot of all emotions, negated emotions are in a seperate graph

```{r}
plot(emo3, facet = 'negated')
```
### Aggregating the sentiment of tweets with that of other topics

#### Downloading tweets of election and president for comparison
```{r}
election_comp1=search_tweets(q='election',n=1000,lang='en',include_rts = FALSE)
pres_comp1=search_tweets(q='president',n=1000,lang='en',include_rts = FALSE)
```

#### Preprocessing for topic 1

```{r}
election_comp1$stripped_text=gsub('[[:punct:]]','',election_comp1$text)
election_comp1$stripped_text=gsub('[[:cntrl:]]','',election_comp1$stripped_text)
election_comp1$stripped_text=gsub('\\d+','',election_comp1$stripped_text)
election_comp1$stripped_text=tolower(election_comp1$stripped_text)
```

#### Preprocessing for topic 2

```{r}
pres_comp1$stripped_text=gsub('[[:punct:]]','',pres_comp1$text)
pres_comp1$stripped_text=gsub('[[:cntrl:]]','',pres_comp1$stripped_text)
pres_comp1$stripped_text=gsub('\\d+','',pres_comp1$stripped_text)
pres_comp1$stripped_text=tolower(pres_comp1$stripped_text)
```

#### Get the sentiment for tweet 1

```{r}
electionc_sent1=sentiment_by(election_comp1$stripped_text)
electionc_sent1
```

#### Getting the summary of the sentiments of the first topic

```{r}
summary(electionc_sent1)
```
```{r}
presc_sent1=sentiment_by(pres_comp1$stripped_text)
presc_sent1
```

#### Getting the summary of the emotions of the second topic

```{r}
summary(presc_sent1)
```

#### Plot sentiments for the topic Election

```{r}
qplot(electionc_sent1$ave_sentiment, xlab = "Sentiment range" , ylab = "Index", geom="histogram",binwidth=0.1,main="Election Sentiment Histogram")


```
 
#### Plot sentiment for the topic President
 
```{r}
qplot(presc_sent1$ave_sentiment, xlab = "Sentiment range", ylab = "Index" ,  geom="histogram",binwidth=0.1,main="President Sentiment Histogram")
```
 
#### Side by side plotfor comparison of the sentiments

```{r}
par(mfrow=c(1,1))
qplot(electionc_sent1$ave_sentiment, xlab = "Sentiment range" , ylab = "Index", geom="histogram",binwidth=0.1,main="Election Sentiment Histogram")
qplot(presc_sent1$ave_sentiment, xlab = "Sentiment range", ylab = "Index" ,  geom="histogram",binwidth=0.1,main="President Sentiment Histogram")

```

## A sentiment comparison between Airbus and Boeing 


#### Loading the tweets from Twitter

```{r}
tweets_airbus=search_tweets(q='airbus',n=1000,lang='en',include_rts = FALSE)
tweets_boeing=search_tweets(q='boeing',n=1000,lang='en',include_rts = FALSE)


```

#### Preprocessing the tweets
```{r}
tweets_airbus$stripped_text=gsub('[[:punct:]]','',tweets_airbus$text)
tweets_airbus$stripped_text=gsub('[[:cntrl:]]','',tweets_airbus$stripped_text)
tweets_airbus$stripped_text=gsub('\\d+','',tweets_airbus$stripped_text)
tweets_airbus$stripped_text=tolower(tweets_airbus$stripped_text)
tweets_boeing$stripped_text=gsub('[[:punct:]]','',tweets_boeing$text)
tweets_boeing$stripped_text=gsub('[[:cntrl:]]','',tweets_boeing$stripped_text)
tweets_boeing$stripped_text=gsub('\\d+','',tweets_boeing$stripped_text)
tweets_boeing$stripped_text=tolower(tweets_boeing$stripped_text)

```

#### Analysis of the tweets

```{r}
sentiment_boeing=sentiment_by(tweets_boeing$stripped_text)
sentiment_boeing
sentiment_airbus=sentiment_by(tweets_airbus$stripped_text)
sentiment_airbus

```

#### Plotting the analysis

```{r}
qplot(sentiment_boeing$ave_sentiment,   geom="histogram",binwidth=0.1,main="boeing Sentiment Histogram")
qplot(sentiment_airbus$ave_sentiment,   geom="histogram",binwidth=0.1,main="airbus Sentiment Histogram")
```

